\documentclass[10pt]{article}
\usepackage{charter}
\usepackage{fullpage}
\usepackage[colorlinks=false]{hyperref}
\usepackage{ifthen}
\usepackage[resetlabels]{multibib}
%\usepackage[openbib,ManyBibs]{currvita}
\usepackage[ManyBibs]{currvita}
%\usepackage{currvita}

\newboolean{doResearchInterests}
%\setboolean{doResearchInterests}{true}
\setboolean{doResearchInterests}{false}

\newcites{refpaper}{foo}
\newcites{unrefpaper}{foo}
\newcites{journal}{foo}
\newcites{techreport}{foo}
\newcites{submitpaper}{foo}
\newcites{classproject}{foo}

% Better for lists with 1-2 items and short descriptions
\newenvironment{sublist}{%
    \begin{list}{}{%
        \setlength{\itemsep}{0em}\setlength{\parsep}{0em}%
        \setlength{\topsep}{0em}\setlength{\parskip}{0em}%
    }%
}%
{ \end{list} }

% Better for lists with more than 2 items and/or long descriptions
\newenvironment{subbulletlist}{%
    \begin{list}{\labelitemii}{%
        \setlength{\topsep}{\itemsep}\setlength{\parskip}{\parsep}%
    }%
}%
{ \end{list} }

\begin{document}

\bibliographystyle{unsrt}
\bibliographystylerefpaper{unsrt}
\bibliographystyleunrefpaper{unsrt}
\bibliographystylesubmitpaper{unsrt}
\bibliographystylejournal{unsrt}
\bibliographystyletechreport{unsrt}
\bibliographystyleclassproject{ieeetr}

\newlength{\oldcvlabelwidth}
\renewcommand*{\cvbibname}{}

\begin{cv}{Matthew J. Miller\\{\large \itshape Curriculum Vitae}}

\begin{cvlist}{Contact}
    \item
    Apex, NC
    \item Phone: Available Upon Request (please email me)
    %\\ Fax: 217-244-5685
    \item \href{mailto:matt@matthewjmiller.net}{matt@matthewjmiller.net}
    \item \href{http://www.matthewjmiller.net/}
    {www.matthewjmiller.net}
\end{cvlist}

\begin{cvlist}{Employment}
    \item[1/2007--present] Software Engineer\\
    Cisco Systems\\
    Research Triangle Park, NC
    \item[1/2003--9/2005] Research Assistant\\
    Coordinated Science Laboratory, University of Illinois at 
    Urbana-Champaign\\
    Urbana, IL
%    \item[1/1998--12/1998] Electrical Engineering Co-op 
%    (\textit{tenure excluded summer months})\\
%    Michelin, North America\\
%    Greenville, SC
\end{cvlist}

\begin{cvlist}{Education}
    \item \emph{Ph.D., Computer Science}, December 2006\\
    University of Illinois at Urbana-Champaign\\
    Urbana, IL
    \begin{sublist}
        \item Thesis: \textit{Energy Efficiency and Security
        for Multihop Wireless Networks}
        \item Adviser: Prof. Nitin H. Vaidya
        \item Committee: Prof. Klara Nahrstedt, Prof. Jennifer Hou,
        and Prof. Indranil Gupta
        \item GPA: 3.94/4.0
    \end{sublist}
    \item \emph{M.S., Computer Science}, December 2003\\ 
    University of Illinois at Urbana-Champaign\\
    Urbana, IL
    \begin{sublist}
        \item Thesis: \textit{Minimizing Energy Consumption in Sensor
        Networks Using a Wakeup Radio}
        \item Adviser: Prof. Nitin H. Vaidya
    \end{sublist}
    \item \emph{B.S., Computer Engineering}, May 2001\\
    Clemson University\\
    Clemson, SC
    \begin{sublist}
        \item GPA: 4.0/4.0
        \item Minors: \emph{Computer Science} and \emph{Mathematics}
    \end{sublist}
\end{cvlist}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Industry Experience}
    \item \textbf{Cisco Systems}
    \begin{subbulletlist}
        \item IOS developer for 7600 router and SIP-400 linecard
        platforms.
        \item Helped implement core dump feature which was a finalist
        for a Reliability, Availability, and Serviceability (RAS) Award
        within business unit.
        \item Sustaining for 7600 IP routing platform code.
        Consistently resolved the most bugs in the group.
        \item Involved in troubleshooting several high profile
        customer cases.
        \item Reviewer for external proposals for Cisco Research.
        \item Served multiple times as a Cisco judge for Duke
        University's graduate networking project class.
    \end{subbulletlist}
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}
%\enlargethispage{0.4in}
%\vspace{-0.5in}

\begin{cvlist}{Honors}
\item%[8/2004--present] 
    \emph{US National Science Foundation Fellowship}
    \begin{sublist}
    \item Awarded in 2001
    \item Acceptance Percentage: 16.2\% (903/5560)
    \end{sublist}
\item%[8/2001--8/2004] 
    \emph{ASEE National Defense Science and 
    Engineering Graduate Fellowship}
    \begin{sublist}
    \item Awarded in 2001
    %\item Acceptance Percentage (2001-2003): 10.2\% (571/5586)
    \item Acceptance Percentage: 21.3\% (285/1339)
    \end{sublist}
\end{cvlist}

%\ifthenelse{\boolean{doResearchInterests}} {
%\pagebreak
%}{}

\ifthenelse{\boolean{doResearchInterests}} {
\begin{cvlist}{Research Interests}
    %\item \textit{Note: Listed in order of preference.}
    \item Network security (both Internet and wireless), 
    %protocol design for wireless devices (e.g., RFIDs and sensors),
    protocol design for wireless devices,
    wireless applications,
    %(particularly focusing on routing and upper layers), 
    peer-to-peer networks.
    %, distributed network-centric applications.

%    \item \textbf{Security and Privacy:} I have done work in sensor security.
%    I am interested in transitioning to network security in
%    general, both Internet and wireless.
%    \item \textbf{Wireless Application and Protocol Design:}  I have
%    an extensive background in multihop wireless networks, particularly
%    with media access control (MAC) and routing protocols.  I am
%    interested in protocol design for devices, such as
%    RFIDs and sensors, that use wireless communications.  In this
%    domain, I would also like to explore new applications for
%    wireless and mobile networks and focus more on routing and upper
%    layers in the network stack.
%    \item \textbf{Peer-to-Peer Networks:} At the routing layer and
%    above, there are many parallels between peer-to-peer and multihop 
%    wireless networks (e.g., limited or no centralized control, finding
%    data and efficiently routing it, dynamic topologies).  Given my
%    research background, I would be interested in researching
%    protocols and system architectures for peer-to-peer networks and, more
%    generally, network-centric applications that could benefit from
%    a distributed design.
\end{cvlist}
} { 
}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\renewcommand*{\bibindent}{1.5em}
% Do bibaddtoleftmargin instead of biblabelsep if you're
% not using manybib or openbib
%\renewcommand*{\bibaddtoleftmargin}{1.5em}
\newcommand*{\biblabelsep}{1.5em}
% To update, before doing latexmk, run:
% bibtex journal
% bibtex refpaper
% bibtex unrefpaper
% bibtex techreport
\begin{cvlist}{Publications}
    \item \textbf{Journal Papers}
    \nocitejournal{sengul08adaptive_vitae}
    \nocitejournal{miller06adhoc_vitae}
    \nocitejournal{miller04mac_vitae}
    \bibliographyjournal{vitae}
    \item \textbf{Conference Papers} 
    \nociterefpaper{miller07practical_vitae}
    \nociterefpaper{miller06leveraging_vitae}
    \nociterefpaper{miller05improving_vitae}
    \nociterefpaper{miller05exploring_vitae}
    \nociterefpaper{miller04power_vitae}
    \nociterefpaper{miller04minimizing_vitae}
    \bibliographyrefpaper{vitae}
    %\item \textbf{Unrefereed Conference Papers} 
    %\nociteunrefpaper{miller04power_vitae}
    %\bibliographyunrefpaper{vitae}

    \ifthenelse{\boolean{doResearchInterests}} {} {
    \pagebreak
    }

    \item \textbf{Submitted Papers} 
    \nocitesubmitpaper{miller05using_vitae}
    \bibliographysubmitpaper{vitae}

    \item \textbf{Technical Reports} 
    \nocitetechreport{miller05errata_vitae}
    \nocitetechreport{miller04ondemand_vitae}
    %\nocitetechreport{miller03thesis}
    \nocitetechreport{miller03hybrid_vitae}
    \bibliographytechreport{vitae}
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Research Experience}
    \item \textbf{Graduate Work}
    \begin{sublist}
        \item 
        My work focuses on \textit{security} and \textit{energy efficiency}
        in wireless
        multihop networks, particularly sensor networks.  In the
        security domain, I proposed a key distribution protocol to
        provide symmetric, pairwise keys that, with high
        probability, are unknown to eavesdroppers.  This was the first
        work to use the underlying wireless channel diversity
        to address this problem.  In the energy efficiency domain, most
        power save protocols use static sleeping and listening intervals
        regardless of the network environment.  My work looks at
        adaptively adjusting these intervals in response to
        network traffic.  Additionally, I have proposed methods of using
        carrier sensing to further improve the energy efficiency of
        power save protocols and a lightweight protocol to address the
        energy-latency tradeoff for broadcast dissemination in sensor
        networks.
%        Some issues I
%        have investigated include key distribution using multiple
%        channels, efficient broadcast in networks using power save
%        protocols, energy-conserving techniques for listening
%        in sleep scheduling
%        protocols, adjusting wake-up schedules based on traffic
%        patterns, and routing metrics to address energy-latency
%        trade-offs.
%        Focus is on the design and simulation of power save
%        protocols in wireless ad-hoc network, especially sensor
%        networks.  We are investigating many issues including
%        coordinating awake times between neighbors, adjusting wake-up
%        schedules based on traffic patterns, assigning channels for
%        waking up neighbors, using multiple power save
%        protocols in a network, and improving IEEE 802.11's ATIM mechanism.
    \end{sublist}

    \item \textbf{Graduate Class Projects}
    \begin{subbulletlist}
        \item \textit{Exploring the Energy-Latency Trade-off of Broadcasts
        in IEEE 802.11 Power Save Networks}\\
        Joint work with Cigdem Sengul in Fall 2003.  
        Designed, analyzed, simulated, and evaluated (using \textit{ns-2}) 
        a protocol for power save networks and the 
        impact of its parameters on energy and latency.  Selected by the
        professor as one of the three best two-person projects in the
        class.  Published in IEEE ICDCS 2005.
        \item \textit{Improving Fault Tolerance in AODV}\\
        Joint work with Jungmin So in Fall 2002.  Designed, simulated,
        and evaluated (using \textit{ns-2})
        techniques to maintain multiple routes in an ad-hoc routing protocol.
        \item \textit{Improving Connectivity in a Scatternet Formation
        Algorithm}\\
        Joint work with Cristina L. Abad in Spring 2002.  Designed,
        simulated, and evaluated (using a custom built simulator written
        in C) a protocol to provide greater
        connectivity in Bluetooth scatternet formation. 
        \item \textit{Log Correlation for Intrusion Detection}\\
        Group project in Spring 2003.  Investigated how information 
        from various system
        logs can be used to identify specific attacks.  Subsequent work 
        by some group members led to a publication based on the
        project:  
        \renewcommand*{\biblabelsep}{1.5em}
        \nociteclassproject{abad03log}
        \bibliographyclassproject{vitae}
        \item \textit{Tools for Middle School Students to Create Vignettes}\\
        Joint work with Jeffrey Naisbitt and Naomi Caldwell in Spring
        2003.  Designed, implemented, and did user-testing on a
        tool (using Java Swing) to allow students to create life 
        stories using an instant messenger-like interface.
    \end{subbulletlist}
    \item \textbf{Awards}
    \begin{subbulletlist}
        \item NSF Student Travel Grant (US \$500) for IEEE BROADNETS 2004 
        \item NSF Student Travel Grant (US \$750) for ACM SenSys 2004
        \item DARPA/NSF Student Travel Grant (US \$400--750) for IEEE MASS 2005
    \end{subbulletlist}
    \item \textbf{Undergraduate Work}
    \begin{subbulletlist}
        \item Participated in the NSF-funded Summer Undergraduate 
        Research Experience (SURE) at Clemson University in 1999.
        \item Worked in Parallel Architecture Research Lab (PARL) 
        at Clemson University for two years.
        \item Projects included designing user interfaces (using Java Swing)
        for scientific
        computing problem solving environments to allow message passing
        between modules and array partitioning.
    \end{subbulletlist}
    \item \textbf{External Reviewer}
    \begin{subbulletlist}
        \item \textit{IEEE Transactions on Mobile Computing}, 
        \textit{IEEE Transactions on Dependable and 
        Secure Computing}, 
        \textit{IEEE Transactions on Wireless Communications}, 
        \textit{IEEE Transactions on Information Forensics and
        Security}, and \textit{IEEE Communications Magazine}.
        \item MobiQuitous 2004, IEEE WCNC 2004, IEEE ICC 2005, 
        IEEE MASS 2006, and IEEE VTC 2006.
        \item Cisco Research funding proposals.
        \item Judge for Duke University Computer Science
        graduate class projects (2007).
    \end{subbulletlist}
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\begin{cvlist}{Memberships}
    \item[1997--present] Member, Institute of Electrical and
    Electronics Engineers (IEEE)
\end{cvlist}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Technical Skills}
    \item \textbf{Proficient}
    \begin{sublist}
        \item C, Python, C++, Java, Perl, LaTeX, Matlab, 
        \textit{ns-2} Network Simulator (C++ based), TinyOS/TOSSIM
    \end{sublist}
    \item \textbf{Familiar} 
    \begin{sublist}
        \item Tcl/Tk, ML, Prolog, Lisp, PHP
    \end{sublist}
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

\begin{cvlist}{Extracurricular}
    \item[2004--2005] Large Group Coordinator\\
    UIUC Graduate InterVarsity Christian Fellowship
    \begin{subbulletlist}
    \item Responsible for contacting and scheduling about 20 
    speakers 
    \item Responsible for arranging facility and equipment
    reservations
    \item Helped restructure the chapter budget
    \end{subbulletlist}
\end{cvlist}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Miscellaneous}
\item \textit{Citizenship:} United States of America
\item \textit{Marital Status:} Married
\item \textit{Erd\"{o}s Number:} $\leq 4$
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}

%\begin{cvlist}{References}
%\item Available upon request
%\item See attached sheets
%\end{cvlist}

\end{cv}
\end{document}

